Sensitivity Analysis

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Model.tex
18.09
11.10

	\subsubsection{Continuity equation} \label{CH: Continuity}
	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{magenta}A_f}(z) = {\color{magenta}A_f\phi}(z)$ to take into account the change of the cross-section available for the fluid. The cross-section change is taken into account by void fraction ${\color{magenta}\phi}(z)$, which depends on the spatial dimension. The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:

	{\footnotesize
		\begin{equation} \label{EQ: Continuity_differential}
			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\phi}(z))}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A\phi}(z))}{\partial {\color{blue}z}} = 0
		\end{equation}
	}
	where ${\color{magenta} A}$ is the total cross-section of the extractor.

	%{\color{red}assign a color of v and u}

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{blue}z}$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A \phi}(z) )}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A\phi}(z)
		\end{equation}
	}

	Here, ${\color{red}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{blue}z}$. To simplify the dynamics of the system, it is assumed that ${\color{red}F}={\color{red}F}(t)$ is a control variable and affects the whole system instantaneously. This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{red}F}(t)$, ${\color{magenta}\phi}(z)$, and ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$.

	{\footnotesize
	\begin{equation}
		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}A\phi}(z)} 
	\end{equation}
	}

	The fluid density ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{blue}P}(t)$ to be constant along ${\color{blue}z}$ due to the low-Mach number condition) are known. The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{blue}z}$ or by a temperature change.

@@

	The detailed derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}). The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform. Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction. Although the particle size distribution and void fraction of the solid phase may change along the extractor, they are assumed to remain constant in time. Furthermore, the thermodynamic pressure is assumed to be constant along the device due to the Low-Mach number condition, as previously discussed. The amount of solute in the solvent is considered negligible, resulting in the fluid phase being described as pseudo-homogeneous, and its properties are assumed to be the same as the solvent. The mass balance equation for the fluid phase includes convection, diffusion, and kinetic terms.

	{\footnotesize
		\begin{equation}
			\label{Model_fluid}
			\frac{\partial {\color{blue}c_f}(t,z)}{\partial t}
			+ \frac{1}{{\color{magenta}\phi}(z)} \frac{\partial \left( {\color{blue}c_f}(t,z) u\right)}{\partial {\color{blue}z}}
			= \frac{1-{\color{magenta}\phi}(z)}{{\color{magenta}\phi}(z)} {\color{blue}r_e}(t,z)
			+ \frac{1}{{\color{magenta}\phi}(z)} \frac{\partial}{\partial {\color{blue}z}} \left( {\color{orange}D^M_e} \frac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}} \right)
		\end{equation}
	}

	Here, ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z),$ and ${\color{blue}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively. ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term, ${\color{red}F}(t)$ is the mass flow rate and ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.

@@

			{\scriptsize
				\begin{equation}
					\begin{aligned}
					&\cfrac{{\color{blue}e}(t,z)-{\color{blue}e}^{id}(t,z)}{R{\color{blue}T}(t,z)} = \\
					& - \cfrac{{\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)\sqrt{8}} \cfrac{{\color{magenta}\kappa} \sqrt{\color{magenta}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)} \right]
					\label{EQ: internal_energy_PR}
				\end{aligned}
			\end{equation}
			}

@@

			{\scriptsize
				\begin{equation}
					\begin{split}
					{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}={\color{magenta}R}{\color{blue}T}(t,z) \left[{\color{magenta}T_r}({\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)-1) \right. \\
					\left. -2.078(1+{\color{magenta}\kappa} ){\sqrt { {\color{orange}\alpha}\left({\color{blue}T}(t,z)\right) } } \ln \left(\cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right)\right]
					\label{EQ:Enthalpy_PR}
				\end{split}
			\end{equation}				
			}

			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{magenta}T_{ref}}=298.15~[K]$ and ${\color{magenta}P_{ref}}=1.01325~[bar]$.

@@

		The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time. As explained in Chapters \ref{CH: Gouverning equations} and \ref{CH:Low_Mach_chapter}, at low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial {\color{blue}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system. The pressure in the system is considered a state variable, while the pressure in the new time-step is considered a control variable.

		{\footnotesize
			\begin{equation}
				\frac{\partial {\color{blue}P}(t)}{\partial t} \approx \frac{{\color{blue}P}(t) - {\color{red}P_{in}}(t) }{\Delta t}
		\end{equation}}

@@

		{\footnotesize
			\begin{align} 
				\label{Model_measurment_1}
%				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
				{\color{blue}y}(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
				\cfrac{d{\color{blue}y}(t)}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
                \label{Model_measurment_2}
		\end{align}	}

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$. On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase. Every SFE system needs some time to reach the desired operating conditions but the solute diffuses from solid phase to the fluid phase already at the preparation stage. For instance, a pump introduce more and more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed. Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}). It can be noticed that each curve at the beginning has a curvature, which is not linear. Generally, a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The details on the calculation are given in Appendix \ref{CH: IC_BC}. The linear distribution $H(z)$ can be defined if the total mass of solute $m_{total}$ and initial mass ratio between solid and fluid phases $\tau$ are known.
		Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$. Therefore, the initial conditions employed in the simulation are:

		{\footnotesize
			\begin{subequations}
				\begin{align*}
					{\color{blue}c_f}(t = 0, z) &= H(z)   \\
					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_{s0}} \\
					{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
				\end{align*}
		\end{subequations} }

@@

		{\footnotesize
			\begin{align}
				\begin{bmatrix}
					\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t}\\
					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t}\\
					\cfrac{\partial {\color{blue}h}(t,z)}{\partial t} \\
					\cfrac{\partial {\color{blue}P}(t,z)}{\partial t} \\
					\cfrac{\partial {\color{blue}y}(t)}{\partial t} 
				\end{bmatrix}
				& =
				\begin{bmatrix}
					{\color{blue}\bar{\phi_1}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
					{\color{blue}\bar{\phi_2}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
					{\color{blue}\bar{\phi_3}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right) \\
					{\color{blue}\bar{\phi_4}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
					{\color{blue}\bar{\phi_5}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
				\end{bmatrix} = {\color{blue}\bar{\phi}} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
		\end{align} }

		where ${\color{magenta}\Theta}$ is a paramter space consisting of model parameters ${\color{magenta}\theta}$ and controls ${\color{red}u}$, ${\color{blue}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.

		Each function ${\color{blue}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{orange}G}_{i\times N_z+1}$ to ${\color{orange}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation. The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$.

			{\footnotesize
				\begin{align*} \label{discretization}
					\dot{{\color{blue}x}}(t) &= \cfrac{d {\color{blue}x}(t)}{d t} = 
					\begin{bmatrix}
						\cfrac{d {\color{blue}c_{f,1}}(t)}{d t} 	  \\
						\vdots					  \\
						\cfrac{d {\color{blue}c_{f,N_z}}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{blue}c_{s,1}}(t)}{d t} 	  \\
						\vdots					  \\
						\cfrac{d {\color{blue}c_{s,N_z}}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{blue}h_1}(t)}{d t} 	  \\
						\vdots 					  \\
						\cfrac{d {\color{blue}h_{N_z}}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{blue}P}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{blue}y}(t)}{d t}
					\end{bmatrix}
					=
					\underbrace{\begin{bmatrix}
							{\color{orange}G_1} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
							\vdots\\ 
							{\color{orange}G_{N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
							\\ \hline \\ \\
							{\color{orange}G_{N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
							\vdots\\
							{\color{orange}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
							\\ \\ \hline \\ 
							{\color{orange}G_{2N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\
							\vdots\\
							{\color{orange}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\ 
							\\ \\ \hline \\
							{\color{orange}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\
							\\ \\ \hline \\
							{\color{orange}G_{3N_z+2}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) 
					\end{bmatrix}}_{{\color{orange}G} \left( {\color{blue}x}(t); {\color{magenta}\Theta} \right)} 
			\end{align*} }

			where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.

>>>>

	\subsubsection{Continuity equation} \label{CH: Continuity}
	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{black}\phi}(z)$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A_f\phi}(z)$ to take into account the change of the cross-section available for the fluid. The cross-section change is taken into account by void fraction ${\color{black}\phi}(z)$, which depends on the spatial dimension. The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:

	{\footnotesize
		\begin{equation} \label{EQ: Continuity_differential}
			\frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\phi}(z))}{\partial t} + \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z))}{\partial {\color{black}z}} = 0
		\end{equation}
	}
	where ${\color{black} A}$ is the total cross-section of the extractor.

	%{\color{black}assign a color of v and u}

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{black}z}$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = 0 \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
		\end{equation}
	}

	Here, ${\color{black}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{black}z}$. To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously. This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{black}F}(t)$, ${\color{black}\phi}(z)$, and ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.

	{\footnotesize
	\begin{equation}
		v = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}A\phi}(z)} 
	\end{equation}
	}

	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known. The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.

@@

	The detailed derivation of the mass balance equation for the fluid phase can be found in the Appendix \ref{CH: Gouverning equations}. The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform. Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction. Although the particle size distribution and void fraction of the solid phase may change along the extractor, they are assumed to remain constant in time. Furthermore, the thermodynamic pressure is assumed to be constant along the device as presented by Equation \ref{EQ: Pressure_Velocity}. The amount of solute in the solvent is considered negligible, resulting in the fluid phase being described as pseudo-homogeneous, and its properties are assumed to be the same as the solvent. The mass balance equation for the fluid phase includes convection, diffusion, and kinetic terms.

	{\footnotesize
		\begin{equation}
			\label{Model_fluid}
			\frac{\partial {\color{black}c_f}(t,z)}{\partial t}
			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial \left( {\color{black}c_f}(t,z) u\right)}{\partial {\color{black}z}}
			= \frac{1-{\color{black}\phi}(z)}{{\color{black}\phi}(z)} {\color{black}r_e}(t,z)
			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial {\color{black}c_f}(t,z)}{\partial {\color{black}z}} \right)
		\end{equation}
	}

	Here, ${\color{black}c_f}(t,z), {\color{black}c_s}(t,z),$ and ${\color{black}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively. ${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, ${\color{black}F}(t)$ is the mass flow rate and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient.

@@

			{\scriptsize
				\begin{equation}
					\begin{aligned}
					&\cfrac{{\color{black}e}(t,z)-{\color{black}e}^{id}(t,z)}{R{\color{black}T}(t,z)} = \\
					& - \cfrac{{\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)} \right]
					\label{EQ: internal_energy_PR}
				\end{aligned}
			\end{equation}
			}

@@

			{\scriptsize
				\begin{equation}
					\begin{split}
					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}{\color{black}T}(t,z) \left[{\color{black}T_r}({\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)-1) \right. \\
					\left. -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left({\color{black}T}(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}\right)\right]
					\label{EQ:Enthalpy_PR}
				\end{split}
			\end{equation}				
			}

			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{black}T_{ref}}=298.15~[K]$ and ${\color{black}P_{ref}}=1.01325~[bar]$.

@@

		The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time. As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system. The pressure in the system is considered a state variable, while the pressure in the new time-step is considered a control variable.

		{\footnotesize
			\begin{equation}
				\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P}(t) - {\color{black}P_{in}}(t) }{\Delta t}
		\end{equation}}

@@

		{\footnotesize
			\begin{align} 
				\label{Model_measurment_1}
%				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
				{\color{black}y}(t) &= \int_{t_0}^{t_f} \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} dt \\
%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
				\cfrac{d{\color{black}y}(t)}{dt} &= \qquad \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} 
                \label{Model_measurment_2}
		\end{align}	}

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$. On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase. Every SFE system needs some time to reach the desired operating conditions but the solute diffuses from solid phase to the fluid phase already at the preparation stage. For instance, a pump introduce more and more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed. Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}). It can be noticed that each curve at the beginning has a curvature, which is not linear. Generally, a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The details on the calculation are given in Appendix \ref{CH: IC_BC}. The linear distribution $H(z)$ can be defined if the total mass of solute $m_{total}$ and initial mass ratio between solid and fluid phases $\tau$ are known.
		Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h_0}$. Therefore, the initial conditions employed in the simulation are:

		{\footnotesize
			\begin{subequations}
				\begin{align*}
					{\color{black}c_f}(t = 0, z) &= H(z)   \\
					{\color{black}c_s}(t = 0, z) &= {\color{black}c_{s0}} \\
					{\color{black}h}(t = 0, z) &= {\color{black}h_0}
				\end{align*}
		\end{subequations} }

@@

		{\footnotesize
			\begin{align}
				\begin{bmatrix}
					\cfrac{\partial {\color{black}c_f}(t,z)}{\partial t}\\
					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t}\\
					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
				\end{bmatrix}
				& =
				\begin{bmatrix}
					{\color{black}\bar{\phi_1}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
					{\color{black}\bar{\phi_2}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
					{\color{black}\bar{\phi_3}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
					{\color{black}\bar{\phi_4}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
					{\color{black}\bar{\phi_5}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)
				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; {\color{black}\Theta} \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
		\end{align} }

		where ${\color{black}\Theta}$ is a paramter space consisting of model parameters ${\color{black}\theta}$ and controls ${\color{black}u}$, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.

		Each function ${\color{black}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}_{i\times N_z+1}$ to ${\color{black}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation. The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.

			{\footnotesize
				\begin{align*} \label{discretization}
					\dot{{\color{black}x}}(t) &= \cfrac{d {\color{black}x}(t)}{d t} = 
					\begin{bmatrix}
						\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
						\vdots					  \\
						\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
						\vdots					  \\
						\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{black}h_1}(t)}{d t} 	  \\
						\vdots 					  \\
						\cfrac{d {\color{black}h_{N_z}}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{black}P}(t)}{d t} \\
						\\ \hline \\
						\cfrac{d {\color{black}y}(t)}{d t}
					\end{bmatrix}
					=
					\underbrace{\begin{bmatrix}
							{\color{black}G_1} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
							\vdots\\ 
							{\color{black}G_{N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
							\\ \hline \\ \\
							{\color{black}G_{N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
							\vdots\\
							{\color{black}G_{2N_z}} \left( {\color{black}c}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
							\\ \\ \hline \\ 
							{\color{black}G_{2N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\
							\vdots\\
							{\color{black}G_{3N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\ 
							\\ \\ \hline \\
							{\color{black}G_{3N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\
							\\ \\ \hline \\
							{\color{black}G_{3N_z+2}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) 
					\end{bmatrix}}_{{\color{black}G} \left( {\color{black}x}(t); {\color{black}\Theta} \right)} 
			\end{align*} }

			where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.

			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$). The controllable input variables are the mass flow-rate and temperature of the solvent in the feed and the pressure in the extractor. Additionally, the pressure change is augumented with the state-space and denoted as ${\color{black}P}(t)$.
			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{black}Y}(t)$). The system is controllable by manipulating the flow-rate and temperature (enthalpy) of $CO_2$ in the feed, and the pressure in the extractor.
